---
title: "MTWAS"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MTWAS)
```

## Step 0: Data Preparation

Load demo TWAS data, which consists of 3 genes and 5 tissues (cell types).

```{r}
data("twas_data")
str(twas_data)
```

## Step 1: Train Weights

Firstly, detect cross-tissue eQTLs,

```{r}
ct.eQTL = select.ct.eQTL(twas_data, verbose = F, ncores = 1)
ct.eQTL
```

One can specify `ncores` for parallel computing. 

Then fix those ct.eQTLs, and select the tissue-specific eQTLs,

```{r}
list.ts.eQTL = select.ts.eQTL(twas_data, ct.eQTL = ct.eQTL, ncores = 1)
list.ts.eQTL
```

By default, it returns the list of ts-eQTLs for each tissue. You can also specify the index of tissue to get the corresponding ts-eQTL,

```{r, eval=FALSE}
select.ts.eQTL(twas_data, ct.eQTL = ct.eQTL, ncores = 1, id.tissue = 1)
```

## Step 2: Association Test

Load GWAS summary statistics for some phenotype

```{r}
data("summary_stats")
str(summary_stats)
```

Then perform an association test in a tissue-specific manner to retain the tissue specificity of the trait-gene associations.

```{r}
twas.single.trait(summary_stats, twas_data, list.ts.eQTL)
```

Alternatively, one can pass a file name to the summary statistics,

```{r, eval=FALSE}
twas.single.trait(twas_data, "/tmp/gwas_summary_stats.txt", list.ts.eQTL)
```

For multiple traits, one can pass a list of summary statistics or files, e.g.,

```{r eval=FALSE}
twas.multiple.trait(twas_data, paste0("/tmp/trait", 1:10, "_gwas_summary_stats.txt"), list.ts.eQTL)
```

